Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-23 src/tex/ms.tex
remove tilde
Added section on GW170818

We carry out \ac{PE} using a custom version of \textsc{Bilby} \citep{Bilby}, that applies Eq.~\eqref{eq:waveform_modification} for any \ac{GR} baseline waveform.
We take the \ac{PE} configuration as in \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset} as a starting point, with \textsc{IMRPhenomXPHM} \citep{Pratten:2020ceb} as the reference waveform.
We apply a distance prior which is uniform in comoving volume and source frame time instead of a power law distribution used in \citep{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, and set the prior on $\kappa$ to a uniform distribution between $-1$ and $1$.

@@

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}.
\begin{table}
    \caption{Events that best constrain $\kappa$. \mi{THOMAS: please just use $\kappa$, no need for the $\tilde{\kappa}$ notation}}
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

@@

% Create sessions for all the outliers

% Case: GW170818
% \subsection{Result on GW170818}

@@

\section{Corner plots of special events}
\label{sec:corner_plots}

>>>>

We carry out \ac{PE} using a custom version of \textsc{Bilby} \citep{Bilby}, that applies Eq.~\eqref{eq:waveform_modification} for any \ac{GR} baseline waveform.
We take the \ac{PE} configuration as in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset} as a starting point, with \textsc{IMRPhenomXPHM} \citep{Pratten:2020ceb} as the reference waveform.
We apply a distance prior which is uniform in comoving volume and source frame time instead of a power law distribution used in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, and set the prior on $\kappa$ to a uniform distribution between $-1$ and $1$.

@@

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}.
\begin{table}
    \caption{Events that best constrain $\kappa$.}
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

@@

% Case: GW170818
\subsection{Result on GW170818}
GW170818 gave the largest tension with $\kappa=0$.
Figure \ref{fig:corner_GW170818} shows the birefringence effect allows a region of $\kappa>0$.
This region corresponds to a larger distance and a smaller inclination angle.
This is a sensible result because a smaller inclination angle will make the amplitude ratio between the two circular polarizations smaller.
Then the birefringence effect will increase the amplitude ratio during the propagation.
The larger distance is for compensating the combined effect of a nonzero $\kappa$ and a smaller inclination angle.
We can see this effect in other events as well, but not as strongly as in GW170818.

@@

\section{Special events}
\label{sec:corner_plots}

\begin{figure}
    \script{corner_GW170818_appendix.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW170818_appendix.pdf}
    \caption{Corner plot of GW170818.}
    \label{fig:corner_GW170818_appendix}
\end{figure}
